Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-09-18 paper/paper.tex
small edit to intro Tested everything on quipu.

\fixme{There are not any direct comparisons of the deterministic and
  stochastic methods that I can find other than the fange2006 paper
  cited above for the round cells.  Those showed that the
  deterministic couldn't predict oscillations in perfectly round
  cells, but could in almost round ellipses.  It seems that once the
  stochastic methods began to be used, nobody really used the
  deterministic method any longer.  Not sure what to say about this in
  order to introduce what we do here properly.}

>>>>

\fixme{There are not any direct comparisons of the deterministic and
  stochastic methods that I can find other than the fange2006 paper
  cited above for the round cells.  Those showed that the
  deterministic sims are 'bistable' - one type of initial conditions
  (MinD starting on walls on one side) show oscillations, another type
  (half cyto is filled with 3/4 of MinD) don't.  Huang in 2004 paper
  cited above uses numerical determinisitc and finds that it can show
  oscillations in round cells as well, but right now I can't find it
  and the journal doesn't give me access to it.  predict oscillations
  in perfectly round cells unless noise was added to the simulation,
  but could in almost round ellipses.  It seems that once the
  stochastic methods began to be used, nobody really used the
  deterministic method any longer.  Not sure what to say about this in
  order to introduce what we do here properly.}
